04-plot characteristics

### 2018-07-30 02_scripts/031-laukiz1-modeling.Rmd
update scripts add prediction script

```{r, results='hide'}
library(mlr)
library(mlrMBO)
library(glue)
library(sf)
library(dplyr)
library(tibble)
library(purrr)
library(magrittr)
library(data.table)
library(pbmcapply)
```

@@

```{r}
data = data[[4]]
coords = coords[[4]]
```

@@

```{r}
task = makeRegrTask(id = "oiartzun", data = data, 
                    target = "defoliation", coordinates = coords)
```

@@

#### SpCV

@@

parallelStop()
saveRDS(resa_rf, "/data/patrick/mod/hyperspectral/spcv/oiartzun_xgboost.rda")
```

>>>>

```{r, results='hide'}
library(mlr)
library(mlrMBO)
library(glue)
library(sf)
library(dplyr)
library(tibble)
library(purrr)
library(magrittr)
library(data.table)
library(stringr)
library(ggpubr)
```

@@

```{r}
data = data[[1]]
coords = coords[[1]]
```

@@

```{r}
task = makeRegrTask(id = "laukiz1", data = data, 
                    target = "defoliation", coordinates = coords)
```

@@

### SpCV

@@

parallelStop()
saveRDS(resa_rf, "/data/patrick/mod/hyperspectral/spcv/laukiz1_xgboost.rda")
```

### 2018-07-30 02_scripts/035-all-plots-modeling.Rmd
update scripts add prediction script

library(mlr)
library(mlrMBO)
library(glue)
library(sf)
library(dplyr)
library(tibble)
library(purrr)
library(magrittr)
library(data.table)
library(pbmcapply)
```

@@

>>>>

library(mlr)
library(mlrMBO)
library(iml)
library(glue)
library(sf)
library(dplyr)
library(tibble)
library(purrr)
library(magrittr)
library(data.table)
library(pbmcapply)
library(ggpubr)
```

@@

#### Train

```{r}
xgboost_tuned = readRDS("/data/patrick/mod/tmp/tuning_hyperspectral/xgboost_tuned_blocking.rda")

lrn_xgboost = setHyperPars(makeLearner("regr.xgboost"), 
                           par.vals = xgboost_tuned$x)
m = train(lrn_xgboost, task)
saveRDS(m, "/data/patrick/mod/hyperspectral/prediction/xgboost_trained_tuned.rda")
```

### Variable importance

#### mlr

We can either use the Feat Imp from `xgboost` by calling `getFeatureImportance()` directly on the fitted model or calculate it again using permutation via `generateFeatureImportanceData()`.

```{r}
# 5h 30 min
var_imp = generateFeatureImportanceData(task, learner = lrn_xgboost, 
                                        measure = rmse, nmc = 2)
saveRDS(var_imp, "/data/patrick/mod/hyperspectral/variable-importance/bf2_ncm2.rda")

var_imp$res = tidyr::gather(var_imp$res, "index", "feat.imp")
var_imp$res %>% 
  arrange(desc(feat.imp)) %>% 
  slice(1:30) %>% 
  ggdotchart(x = "index", y = "feat.imp",                              # Color by groups
             sorting = "asc",                       # Sort value in descending order
             add = "segments",                             # Add segments from y = 0 to dots
             #color = "index",
             palette = "nejm",
             #position = position_dodge(1),
             group = "index",
             #title = .y,
             rotate = T,                                # Rotate vertically
             dot.size = 0.5,                                 # Large dot size
             ggtheme = theme_pubr(base_size = 6, margin = F,
                                  legend = "none")) + 
  labs(y = "Score", color = "Spectral region")
```

Visualize top 30 indices

```{r}
imp.xgb = getFeatureImportance(m) 
imp.xgb$res = tidyr::gather(imp.xgb$res, "index", "feat.imp")

imp.xgb$res %>% 
  arrange(desc(feat.imp)) %>% 
  slice(1:30) %>% 
  ggdotchart(x = "index", y = "feat.imp",                              # Color by groups
             sorting = "asc",                       # Sort value in descending order
             add = "segments",                             # Add segments from y = 0 to dots
             #color = "index",
             palette = "nejm",
             #position = position_dodge(1),
             group = "index",
             #title = .y,
             rotate = T,                                # Rotate vertically
             dot.size = 0.5,                                 # Large dot size
             ggtheme = theme_pubr(base_size = 6, margin = F,
                                  legend = "none")) + 
  labs(y = "Score", color = "Spectral region")
```
```{r}
ggsave(here::here("03_figures/results/var-imp-xgboost.png"), height = 3,
       width = 5)
```

#### iml

```{r}
X = task$env$data[which(names(task$env$data) != "defoliation")]
predictor = Predictor$new(m, data = X, y = task$env$data$defoliation)
imp = FeatureImp$new(predictor, loss = "rmse")
```

Partial influence

```{r}
X = task$env$data[which(names(task$env$data) != "defoliation")]
predictor = Predictor$new(m, data = X, y = task$env$data$defoliation)
pdp.obj = Partial$new(predictor, feature = "bf2_EVI")
pdp.obj$plot()
```

### 2018-07-30 02_scripts/04_plot_characteristics.Rmd
update scripts add prediction script

```{r}
data %>%
  group_by(plot) %>%
  summarise(mean(defoliation))
```

@@

```{r}
data %>%
  group_by(plot) %>%
  summarise((sd(defoliation) / mean(defoliation)) * 100)
```

@@

```{r}
data %>%
  group_by(plot) %>%
  summarise(((sd(defoliation) / mean(defoliation)) * 100) / e1071::skewness(defoliation))
```

```{r}
data %>%
  group_by(plot) %>%
  summarise(sd(defoliation))
```

@@

  distance <- mean(as.dist(pointDistance(points, allpairs = TRUE, lonlat = FALSE)))
})
set_names(dist, plots)
```

@@

```{r}
df <- tibble(
  plot = factor(c("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun")),
  rmse = c(89.89, 30.37, 76.02, 106.65),
  point_dens = c(34.34, 62.51, 33.76, 35.01),
  mean_defol = c(53.22, 17.73, 68.35, 44.63),
  cov_defol = c(44.88707	, 115.78180	, 12.17709	, 83.18840),
  sd_skewness = c(-55.077546, 67.232146, -3.187733	, -401.564010)
)
```

>>>>

```{r}
mean_defol = data %>%
  group_by(plot) %>%
  summarise(mean(defoliation)) %>% 
  pull(.)

data %>%
  group_by(plot) %>%
  summarise(mean(defoliation))
```

@@

```{r}
cov_defol = data %>%
  group_by(plot) %>%
  summarise((sd(defoliation) / mean(defoliation)) * 100) %>% 
  pull(.)

data %>%
  group_by(plot) %>%
  summarise((sd(defoliation) / mean(defoliation)) * 100)
```

@@

```{r}
sd_skewness_defol = data %>%
  group_by(plot) %>%
  summarise(((sd(defoliation) / mean(defoliation)) * 100) / e1071::skewness(defoliation)) %>% pull(.)

data %>%
  group_by(plot) %>%
  summarise(((sd(defoliation) / mean(defoliation)) * 100) / e1071::skewness(defoliation))
```

```{r}
sd_defol = data %>%
  group_by(plot) %>%
  summarise(sd(defoliation)) %>% 
  pull(.)

data %>%
  group_by(plot) %>%
  summarise(sd(defoliation))
```

@@

  distance <- mean(as.dist(pointDistance(points, allpairs = TRUE, lonlat = FALSE)))
})
set_names(dist, plots)

dist_plots = unlist(dist)
```

@@

## Load CV results

```{r}
laukiz1 = readRDS("/data/patrick/mod/hyperspectral/spcv/laukiz1_xgboost.rda")
laukiz2 = readRDS("/data/patrick/mod/hyperspectral/spcv/laukiz2_xgboost.rda")
luiando = readRDS("/data/patrick/mod/hyperspectral/spcv/luiando_xgboost.rda")
oiartzun = readRDS("/data/patrick/mod/hyperspectral/spcv/oiartzun_xgboost.rda")

models <- list(laukiz1, laukiz2, luiando, oiartzun)

results_reps <- map(models, ~ .x$measures.test %>% 
                      dplyr::mutate(rep = rep(1:5, times = 1, each = 5)) %>% 
                      group_by(rep) %>% 
                      summarise_at("rmse", mean),
)
results_reps <- set_names(results_reps, 
                          c("laukiz1", "laukiz2", "luiando", "oiartzun"))
```

```{r}
df <- tibble(
  plot = factor(c("Laukiz 1", "Laukiz 2", "Luiando", "Oiartzun")),
  rmse = c(mean(results_reps$laukiz1), mean(results_reps$laukiz2), mean(results_reps$luiando), mean(results_reps$oiartzun)),
  point_dens = dist_plots,
  mean_defol = mean_defol,
  cov_defol = cov_defol,
  sd_skewness = sd_skewness_defol
)
```
